Scikit-learn: machine learning without learning the machinery

### 2014-07-01 article.tex
prediction "of some value of interest" (XXX or variable?)
cosmit

\paragraph{The Python data ecosystem.}
%
Machine learning is only a small part of a data-analysis pipeline, and
scikit-learn nicely dovetails into the rich Python ecosystem: scientific
and numeric tools \cite{oliphant2007python,varoquaux2013scipy}, but also
text processing tools, web servers...
%
For its numerical needs, scikit-learn leverages NumPy arrays
\cite{vanderwalt2011} --data structures for efficient numerical
computation--, SciPy --a collection of classic numerical algorithms--,
matplotlib \cite{hunter2007matplotlib} --for scientific plotting-- and
Cython, to generate and call compiled code in a Python-like syntax
\cite{behnel2011cython}.
%
A plethora of Python packages can help users with input or preprocessing
of data, notably Pandas for columnar data \cite{mckinney2012}, scikit-image
for images, and NLTK for text. Finally, the IPython environment
\cite{perez2007ipython} is priceless for interactive work.

@@

\paragraph{Supervised models: learning to predict.}
%
The goal of supervised models is prediction. The corresponding estimators
have a {\tt predict} method, that takes a data matrix $\mathbf{X}$ and
returns a predicted $\mathbf{y}$.

>>>>

\paragraph{The Python data ecosystem.}
%
Machine learning is only a small part of a data-analysis pipeline, and
scikit-learn nicely dovetails into the rich Python ecosystem: scientific
and numeric tools \cite{oliphant2007python,varoquaux2013scipy}, but also
text processing tools, web servers, etc.
%
For its numerical needs, scikit-learn leverages NumPy arrays
\cite{vanderwalt2011} --data structures for efficient numerical
computation--, SciPy --a collection of classic numerical algorithms--,
matplotlib \cite{hunter2007matplotlib} --for scientific plotting-- and
Cython, to generate and call compiled code in a Python-like syntax
\cite{behnel2011cython}.
%
A plethora of Python packages can help users with input or preprocessing
of data, notably Pandas for columnar data \cite{mckinney2012}, scikit-image
for images, and NLTK for text. Finally, the IPython environment
\cite{perez2007ipython} is priceless for interactive work.

@@

\paragraph{Supervised models: learning to predict.}
%
The goal of supervised models is prediction of some value of interest.
The corresponding estimators
have a {\tt predict} method, that takes a data matrix $\mathbf{X}$ and
returns a predicted $\mathbf{y}$.
